---
title: Release notes of package wyz.code.offensiveProgramming
author: Fabien GELINEAU
date: 2019-07-10
output: rmarkdown::html_vignette
css: style.css
vignette: >
  %\VignetteIndexEntry{ Release notes of package wyz.code.offensiveProgramming }
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# wyz.code.offensiveProgramming 1.01.001

## Content

```{r echo = FALSE}
pkgn <- 'wyz.code.offensiveProgramming'
sf <- system.file('life-cycle/data-1.01.001.rds', package = pkgn)
dt_1.01.001 <- readRDS(sf)
DT::datatable(dt_1.01.001, options(paging = FALSE))
```

## Changes

1. package elaboration

## Identification

major [asterion] minor [awesome] fix [alpha] timestamp [2019-07-03 18:36:19] number [1.01.001]

# wyz.code.offensiveProgramming 1.01.002

## Content

```{r echo = FALSE}
pkgn <- 'wyz.code.offensiveProgramming'
sf <- system.file('life-cycle/data-1.01.002.rds', package = pkgn)
dt_1.01.002 <- readRDS(sf)
DT::datatable(dt_1.01.002, options(paging = FALSE))
```

## Changes

1. Alignement of vignette onto online offensive programming book
1. release new bundle for CRAN submission

## Identification

major [asterion] minor [awesome] fix [beta] timestamp [2019-07-03 18:38:00] number [1.01.002]

# wyz.code.offensiveProgramming 1.01.003

## Content

```{r echo = FALSE}
pkgn <- 'wyz.code.offensiveProgramming'
sf <- system.file('life-cycle/data-1.01.003.rds', package = pkgn)
dt_1.01.003 <- readRDS(sf)
DT::datatable(dt_1.01.003, options(paging = FALSE))
```

## Changes

1. removed undesirable dependency against wyz.code.ops

## Identification

major [asterion] minor [awesome] fix [gamma] timestamp [2019-07-03 20:39:14] number [1.01.003]

# wyz.code.offensiveProgramming 1.01.004

## Content

```{r echo = FALSE}
pkgn <- 'wyz.code.offensiveProgramming'
sf <- system.file('life-cycle/data-1.01.004.rds', package = pkgn)
dt_1.01.004 <- readRDS(sf)
DT::datatable(dt_1.01.004, options(paging = FALSE))
```

## Changes

1. Changed description version as leading zeros are forbidden by CRAN.

## Identification

major [asterion] minor [awesome] fix [delta] timestamp [2019-07-04 09:32:26] number [1.01.004]

# wyz.code.offensiveProgramming 1.01.005

## Content

```{r echo = FALSE}
sf <- system.file("life-cycle/data-1.01.005.rds", package = "wyz.code.offensiveProgramming")
ds <- readRDS(sf)
DT::datatable(ds, options(paging = FALSE))
```

## Changes

1. Changed retrieveFactory code. Remove global environment assignment as requested by CRAN 

## Identification

major [asterion] minor [awesome] fix [epsilon] timestamp [2019-07-10 21:11:33] number [1.01.005]

